On existence of integral point sets and their diameter bounds \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2020-03-25 pps-linear-bound/pps-linear-lower-bound.tex
[J220] Avoid dashes next to formulas

	a) $N$ belongs to $C$~--- overall at most $\gamma_2 b + 6$ points by Lemma~\ref{lem:intervals_cross} and Proposition~\ref{obs:estimate_points_on_straight_line};

	b) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas
	with one of $|M_3 M_4| - 1$ hyperbolas~--- overall at most $4 (|M_1 M_2| - 1)(|M_3 M_4| - 1)$ points;

	c) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas with $cr(M_3 M_4)$~---
	overall at most $4 (|M_1 M_2| - 1)$ points;

	d) $N$ belongs to the intersection of one of $|M_3 M_4| - 1$ hyperbolas with $cr(M_1 M_2)$~---
	overall at most $4 (|M_3 M_4| - 1)$ points;

	(see~\cite{erdos1945integral} for details).
	Summing up the above cases, we obtain the following estimate:
	\begin{equation}
		\label{eq:estimate_n_varphi_n_squared}
		n \leq 4 b^2 \varphi_{n-1}^2 - 4 + \gamma_2 b + 6
		.
	\end{equation}
	Proposition~\ref{varphi_n_where_n_geq_21492} turns estimate~\eqref{eq:estimate_n_varphi_n_squared}
	into the following:
	\begin{equation}
		\label{eq:estimate_n_sqrt_n-2}
		n-2 \leq 4 b^2 \frac{\beta^2}{n-2} + \gamma_2 b
		,
	\end{equation}
	which obviously leads to inequality
	\begin{equation}
		1 \leq 4\beta^2 \left(\frac{b}{n-2}\right)^2  + \gamma_2 \frac{b}{n-2}
		.
	\end{equation}
	Let us denote $\lambda = b/(n-2)$ and solve the following quadratic inequality for $\lambda$:
	\begin{equation}
		\label{eq:square_inequality_lambda}
		4\beta^2 \lambda^2  + \gamma_2 \lambda - 1 \geq 0
		.
	\end{equation}
	The discriminant is $\gamma_2^2 + 16 \cdot \beta^2$,
	so we obtain the following estimate:
	\begin{equation}
		\frac{b}{n-2} = \lambda \geq \frac{-\gamma_2 + \sqrt{\gamma_2^2 + 16 \cdot \beta^2}}{8\beta^2}
		.
	\end{equation}
	Calculating the expression above for our $\beta$ and $\gamma_2$, we conclude the proof.
\end{proof}

>>>>

	a) $N$ belongs to $C$; overall at most $\gamma_2 b + 6$ points by Lemma~\ref{lem:intervals_cross} and Proposition~\ref{obs:estimate_points_on_straight_line};

	b) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas
	with one of $|M_3 M_4| - 1$ hyperbolas; overall at most $4 (|M_1 M_2| - 1)(|M_3 M_4| - 1)$ points;

	c) $N$ belongs to the intersection of one of $|M_1 M_2| - 1$ hyperbolas with $cr(M_3 M_4)$;
	overall at most $4 (|M_1 M_2| - 1)$ points;

	d) $N$ belongs to the intersection of one of $|M_3 M_4| - 1$ hyperbolas with $cr(M_1 M_2)$;
	overall at most $4 (|M_3 M_4| - 1)$ points;
	\\
	(see~\cite{erdos1945integral} for details).
	Summing up the above cases, we obtain the following estimate:
	\begin{equation}
		\label{eq:estimate_n_varphi_n_squared}
		n \leq 4 b^2 \varphi_{n-1}^2 - 4 + \gamma_2 b + 6
		.
	\end{equation}
	Proposition~\ref{varphi_n_where_n_geq_21492} turns estimate~\eqref{eq:estimate_n_varphi_n_squared}
	into the following:
	\begin{equation}
		\label{eq:estimate_n_sqrt_n-2}
		n-2 \leq 4 b^2 \frac{\beta^2}{n-2} + \gamma_2 b
		,
	\end{equation}
	which obviously leads to inequality
	\begin{equation}
		1 \leq 4\beta^2 \left(\frac{b}{n-2}\right)^2  + \gamma_2 \frac{b}{n-2}
		.
	\end{equation}
	Let us denote $\lambda = b/(n-2)$ and solve the following quadratic inequality for $\lambda$:
	\begin{equation}
		\label{eq:square_inequality_lambda}
		4\beta^2 \lambda^2  + \gamma_2 \lambda - 1 \geq 0
		.
	\end{equation}
	The discriminant is $\gamma_2^2 + 16 \cdot \beta^2$,
	so we obtain the following estimate:
	\begin{equation}
		\frac{b}{n-2} = \lambda \geq \frac{-\gamma_2 + \sqrt{\gamma_2^2 + 16 \cdot \beta^2}}{8\beta^2}
		.
	\end{equation}
	Calculating the expression above for our $\beta$ and $\gamma_2$, we conclude the proof.
\end{proof}
